### 2019-08-27 reports/thesis/chapters/5_inference.tex
Adjust defectdetect
ROC area use 1000 points
Made commment on ROC integration

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_roc.eps}
        \caption{Dust defect $\pi_1=0.1$, $r=20$}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_roc.eps}
        \caption{5 pixels thick line defect, $r=20$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_roc.eps}
        \caption{$30\times 30$ square defect, $r=20$}
        \label{fig:inference_defectSimulationRoc_square20}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_roc.eps}
        \caption{$30\times 30$ square defect, $r=40$}
      \end{subfigure}
    }
  \caption{ROC curves for various defected $256\times 256$ Gaussian images. The upper/lower dashed line show the resulting ROC curve when testing on an image without/with contamination respectively. The different curves are the resulting ROC curves after filtering a contaminated image. Defected pixels have the distribution $\normal(3,1)$. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
  \label{fig:inference_defectSimulationRoc}
\end{figure}

@@

An experiment was conducted to investigate the specificity of the test before and after filtering. A $256\times 256$ Gaussian image with speckle defect with density $\pi_1=0.1$ and various values of $\mu_1$ were investigated. The AUC, type 1 error, type 2 error and FDR were measured when testing on an image with a defect before and after contamination and then after filtering with the contamination. A kernel radius of $r=20$ was used and was repeated 100 times by simulating another image.

@@

An experiment was conducted where the contaminated defected image were filtered for various kernel radiuses for a fixed alternative distribution $\normal(3,1)$. Hypothesis testing was done on the uncontaminated and filtered contaminated image and the AUC and various errors were recorded, this was repeated 100 times. The results of the uncontaminated image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination. Results for the line and square defect are shown in Figures \ref{fig:inference_Experiment_DefectRadiusLine} and \ref{fig:inference_Experiment_DefectRadiusSquare} respectively.

>>>>

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_roc.eps}
        \caption{Dust defect $\pi_1=0.1$, $r=20$}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_roc.eps}
        \caption{5 pixels thick line defect, $r=20$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_roc.eps}
        \caption{$30\times 30$ square defect, $r=20$}
        \label{fig:inference_defectSimulationRoc_square20}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_roc.eps}
        \caption{$30\times 30$ square defect, $r=40$}
      \end{subfigure}
    }
  \caption{ROC curves for various defected $256\times 256$ Gaussian images. The upper/lower dashed line show the resulting ROC curve when testing on an image without/with contamination respectively. The different curves are the resulting ROC curves after filtering a contaminated image. Defected pixels have the distribution $\normal(3,1)$. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$.}
  \label{fig:inference_defectSimulationRoc}
\end{figure}

@@

An experiment was conducted to investigate the specificity of the test before and after filtering. A $256\times 256$ Gaussian image with speckle defect with density $\pi_1=0.1$ and various values of $\mu_1$ were investigated. The AUC, type 1 error, type 2 error and FDR were measured when testing on an image with a defect before and after contamination and then after filtering with the contamination. The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1000 trapeziums. A kernel radius of $r=20$ was used and was repeated 100 times by simulating another image.

@@

An experiment was conducted where the contaminated defected image were filtered for various kernel radiuses for a fixed alternative distribution $\normal(3,1)$. Hypothesis testing was done on the uncontaminated and filtered contaminated image and the AUC and various errors were recorded, this was repeated 100 times. The AUC was obtained by numerically integrating the ROC curve using the trapezium rule with 1000 trapeziums. The results of the uncontaminated image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination. Results for the line and square defect are shown in Figures \ref{fig:inference_Experiment_DefectRadiusLine} and \ref{fig:inference_Experiment_DefectRadiusSquare} respectively.
